\chapter{Conclusion \& Future Enhancements}
\section{Conclusion}
sample conclusion given
write about your project
Insight – A key aspect of a doctor appointment booking system is ensuring that the database is able to handle a high volume of concurrent users and transactions. This may require implementing techniques such as load balancing and indexing to optimize performance.

It is important to consider data security and privacy when designing the database. This may include implementing encryption for sensitive information such as patient medical records and ensuring that only authorized users have access to the system.
The database should be designed to be easily integrated with other systems, such as electronic medical record systems and billing systems, to streamline workflows and improve efficiency.
The system should be able to handle different types of appointment scheduling, such as recurring appointments, walk-in appointments, and online bookings.
The system should be able to handle various types of patients, such as children and elderly, with different needs and preferences.
The system should be able to handle different types of doctors, such as specialists, and different languages and communication needs.

In conclusion, a doctor appointment booking system database project requires careful planning and consideration of various factors to ensure its effectiveness and efficiency. The database must be able to handle a high volume of concurrent users and transactions, as well as ensure data security and privacy. It should also be easily integrated with other systems and able to handle different types of appointments, patients, doctors, insurance, clinics, location and time zones. Additionally, an effective user interface and regular testing and maintenance are crucial for the success of the system. With careful attention to these details, the doctor appointment booking system database can be a valuable tool for streamlining appointments, improving patient care, and supporting the work of medical professionals.

\section{Future Enhancements}
Some of the future works include,
\begin{itemize}
    \item saves patients' history and guide for some basic medications
    \item live-track patients in order of appointments and decides the exact time at which one has to board from the location to hospital based on the distance of the appointed doctor's hospital location.
    \item Provide patients with all the previous records and maintain them.
    \item Suggesting surgeons and nearby hospitals according to patients' problems.
    \item AI-based First Aid solutions for immediate actions.
    
\end{itemize}


